### 2017-03-20 intro.tex
new ref

%!TEX root =  autocontgrlp.tex
\section{Introduction}
Markov decision processes (MDPs) have proved to be an indispensable model for sequential decision making under uncertainty with applications in networking, traffic control, robotics, operations research, business, finance, artificial intelligence, health-care and more (see, e.g., \cite{BauRie:11,Puter,FeiSh02:MDPHandbook,Abuetal15:MDPWireless,White93:Apps,QiWu07,SiBu10:MDPinAI}).
The main objective in planning with MDPs is to compute actions of a policy that maximizes cumulated reward over time.
While this can be done in time that scales polynomially with the number of states and actions using various algorithms
\cite{BlonTsi:00Complexity}, in most practical applications, 
the MDPs are described using a ``succinct'' representation and the number of states (and sometimes actions) then scale exponentially with the size of the representation. For specific such MDPs various hardness results show that the
goal of computing near-optimal policies is impractical.
One approach then is to change the goal to the more modest goal of efficiently computing actions of a policy that 
is nearly as good as the best policy in a given restricted policy class.
The choice of the policy class, within some limits, is left to the user. 
Stronger methods give more flexibility to the user in choosing the policy class.

>>>>

%!TEX root =  autocontgrlp.tex
\section{Introduction}
Markov decision processes (MDPs) have proved to be an indispensable model for sequential decision making under uncertainty with applications in networking, traffic control, robotics, operations research, business, finance, artificial intelligence, health-care and more (see, e.g., \cite{BauRie:11,Puter,FeiSh02:MDPHandbook,Abuetal15:MDPWireless,White93:Apps,QiWu07,SiBu10:MDPinAI,BouDi17:MDPPractice}).
The main objective in planning with MDPs is to compute actions of a policy that maximizes cumulated reward over time.
While this can be done in time that scales polynomially with the number of states and actions using various algorithms
\cite{BlonTsi:00Complexity}, in most practical applications, 
the MDPs are described using a ``succinct'' representation and the number of states (and sometimes actions) then scale exponentially with the size of the representation. For specific such MDPs various hardness results show that the
goal of computing near-optimal policies is impractical.
One approach then is to change the goal to the more modest goal of efficiently computing actions of a policy that 
is nearly as good as the best policy in a given restricted policy class.
The choice of the policy class, within some limits, is left to the user. 
Stronger methods give more flexibility to the user in choosing the policy class.
